Verifying Demonstrations

### 2017-10-04 protocol.tex
Renames labels of figs, adds stub for protocol diagram

An overview of the structure of a proof is available in \cref{ProofFig}.

\begin{frame}
\begin{figure}
  \centering
  \begin{tikzpicture}
    \tikzset{grow'=left,level distance=5em}
    \Tree [.proof
    {share}
    [.{share} {\(wid\)} {\(l\)} {$t_s$} [.{\(pid\)} [.{\(cid\)} manifesto ] ]
    %[.tsig {$t_s''$} ]
    ]
    {share}
    ]
  \end{tikzpicture}
  \mode<article>{%
  \caption{%
    The proof depends on several proof shares.
    Each share depends on the protester's identifier (\(pid\), which depends on 
    the cause identifier, \(cid\)),
    the head of the blockchain (\(t_s\)), the location (\(l\)) and the witness 
    identifier (\(wid\)).
  }}%
  \label{ProofFig}
\end{figure}
\end{frame}

@@

We will start with the latter.
The identifier of the protest must be regulated, for the same reasons as for the 
user identifiers --- otherwise a counter-protest can simply choose the same 
protest identifier.
As was pointed out in \cref{CauseIsTheCommonDenominator}, the cause is at the 
root of what defines a protest.
The cause can be captured in some sort of \enquote{manifesto}, thus, we will use 
the hash value of the manifesto as identifier of the protest (cause).
(As shown as manifesto and cause identifier \(cid\) in \cref{ProofFig}.)

@@

Given the properties of the storage (in \cref{StorageProperties}), for 
\cref{CreatedAfterStart}, Alice and Bob must include the hash value of an 
existing block in the blockchain in each proof share (shown as \(t_s\) in 
\cref{ProofFig}).
Then it is clear that the proof must have been created after that block (since 
predicting such a value is hard).

>>>>

An overview of the final structure of a proof is given in \cref{fig:ProofFig} 
and an overview of the communication is given in \cref{fig:ProtocolOverview}.

\begin{frame}
\begin{figure}
  \centering
  \begin{tikzpicture}
    \tikzset{grow'=left,level distance=5em}
    \Tree [.proof
    {share}
    [.{share} {\(wid\)} {\(l\)} {$t_s$} [.{\(pid\)} [.{\(cid\)} manifesto ] ]
    %[.tsig {$t_s''$} ]
    ]
    {share}
    ]
  \end{tikzpicture}
  \mode<article>{%
  \caption{%
    The proof depends on several proof shares.
    Each share depends on the protester's identifier (\(pid\), which depends on 
    the cause identifier, \(cid\)),
    the head of the blockchain (\(t_s\)), the location (\(l\)) and the witness 
    identifier (\(wid\)).
  }}%
  \label{fig:ProofFig}
\end{figure}
\end{frame}

\begin{figure}
  \centering
  \dots
  \caption{%
    \dots
  }%
  \label{fig:ProtocolOverview}
\end{figure}

@@

We will start with the latter.
The identifier of the protest must be regulated, for the same reasons as for the 
user identifiers --- otherwise a counter-protest can simply choose the same 
protest identifier.
As was pointed out in \cref{CauseIsTheCommonDenominator}, the cause is at the 
root of what defines a protest.
The cause can be captured in some sort of \enquote{manifesto}, thus, we will use 
the hash value of the manifesto as identifier of the protest (cause).
(As shown as manifesto and cause identifier \(cid\) in \cref{fig:ProofFig}.)

@@

Given the properties of the storage (in \cref{StorageProperties}), for 
\cref{CreatedAfterStart}, Alice and Bob must include the hash value of an 
existing block in the blockchain in each proof share (shown as \(t_s\) in 
\cref{fig:ProofFig}).
Then it is clear that the proof must have been created after that block (since 
predicting such a value is hard).
